\section{Realized volatility}
    Consider a stochastic volatility model 
    \begin{equation}\label{model:SVM}
        dS_t = \mu_t S_t dt + \sigma_t S_tdW_t,
    \end{equation}
    where $S_t$ is an asset price process, and $\sigma_t$ is a stochastic volatility process representing a so-called \emph{spot volatility}.
    Spot volatility, in fact, is not observable in the market, therefore, we should estimate it somehow.

    \begin{definition}
        The \emph{realized variance} of a price process $S$ over time interval $[t, t + \delta]$ sampled along the time partition $\pi^n$
        is defined as 
        \begin{equation}\label{def:RV}
            RVar_{t, t + \delta}(\pi^n) = \sum_{\pi^n \cap [t, t + \delta]} \left(\log S_{t^n_{i+1}} - \log S_{t^n_{i}}\right)^2
        \end{equation}
        and \emph{realized volatility} is defined as
        \begin{equation}\label{def:RVol}
            RV_{t, t + \delta}(\pi^n) = \sqrt{\sum_{\pi^n \cap [t, t + \delta]} \left(\log S_{t^n_{i+1}} - \log S_{t^n_{i}}\right)^2}
        \end{equation}
    \end{definition}

    \begin{definition}
        Let $S$ satisfy \eqref{model:SVM}. Then the integrated variance is defined as
        \begin{equation}\label{def:IV}
            IVar_t = \int_{0}^{t} \sigma_s^2 ds
        \end{equation}
    \end{definition}
    It has been shown many times (e.g. \cite{Barndorff-Nielsen2002}) and mentioned in \cite{Cont2022} that the realized variance converges 
    in probability to the integrated variance as sampling frequency increases for all assets satistying the equation 
    \eqref{model:RFSVasset} (i.e. stochastic volatility models).
    \begin{proposition} 
        As time partition scale of $\pi^n$ tends to $0$, $RV_{t, t + \delta}(\pi^n) \approx \sqrt{\delta} \sigma_t$, i.e. $RV_{t, t + \delta}/\sqrt{\delta}$ could be considered as a consistent estimator of the spot volatility.
    \end{proposition}

    \begin{definition}
        The \emph{fractional Brownian motion} $(W_t^H)_{t\in \mathbb{R_+}}$ with Hurst 
        parameter $H \in (0, 1)$ is a Gaussian process with the following properties:
        \begin{enumerate}
            \item $W_0^H = 0$,
            \item $\mathbb{E}\left[W_t^H\right] \equiv 0$,
            \item $\mathbb{E}\left[W_s^H W_t^H\right] = \frac{1}{2} \left(t^{2H} + s^{2H} - |t-s|^{2H}\right)$
        \end{enumerate}
    \end{definition}

    \begin{definition}
        A stationary fOU process $X_t$ is defined as the stationary solution of the stochastic differential equation
        \begin{equation}
            dX_t = \nu dW^H_t - \alpha (X_t - m)dt,
        \end{equation}
        where $m \in \mathbb{R}$ and $\nu$ and $\alpha$ are positive parameters, see \cite{Cheridito2003}.
    \end{definition}

    \subsection{What is a long-memory process?}
        \begin{definition}
            A process $X_t$ is said to have a long memory, if 
            \begin{equation}
                \sum_{k=0}^{\infty}Cov\left[X_1 , X_{k} - X_{k-1}\right] = +\infty.
            \end{equation}
        \end{definition}

        In particular, the fractional Brownian motion with $H > \frac{1}{2}$ is a long-memory process.
        Long-memory of the stochastic volatility process in stochastic volatilty models framework used to be a 
        widely-accepted stylized fact \cite{Breidt1998,ComteRenault1998,Comte1996,Ding1993}.

\section{Model description}
    In \cite{GatheralRosenbaum2014} the authors considered the following model, as did I. 
    Let there be a riskless asset $B_t \equiv 1$, and a risky asset, whose price $S_t$ is defined 
    by the following equations: 
    \begin{align}
        & dS_t          = \alpha S_t dt + \sigma_t S_tdW_t,               \label{model:RFSVasset} \\
        & d\log\sigma_t = \alpha (m - \log\sigma_t) dt + \nu dW_t^H,      \label{model:RFSVvol}
    \end{align}
    The risky asset is being traded in the market in numeraire prices (in our case, $B_t = 1$ RUB for stocks and GBP for depositary reciepts).
    \begin{definition}
        A model \eqref{model:RFSVasset} -- \eqref{model:RFSVvol} is called a 
        \emph{Fractional Stochastic Volatility Model}\footnote{Despite the original \cite{ComteRenault1998} 
        naming (Comte and Renault used a model with long memory of volatility as a stylized fact), we shall 
        call our model FSV for any $H \in (0, 1)$} (FSV). For a special case $H < 0.5$ the 
        model is called a \emph{Rough Fractional Stochastic Volatility Model} (RFSV) to emphasise a 
        so-called roughness of the trajectories of the fBm.
    \end{definition}

    In \cite{Cheridito2003} an exact formula for the autocovariance function of the log-volatility in the RFSV model was derived:
    \begin{multline}\label{formula:CovLog}
        \cov\left[\log \sigma_{t}, \log \sigma_{t+\Delta}\right] =\\= \frac{H(2H-1)\nu^2}{2\alpha^{2H}}\left(e^{-\alpha\Delta} \Gamma(2H-1) + e^{-\alpha\Delta} \int_{0}^{\alpha\Delta}\frac{e^u}{u^{2-2H}}du + e^{\alpha\Delta} \int_{\alpha\Delta}^{+\infty}\frac{e^u}{u^{2-2H}}du\right)
    \end{multline}

    Via the explicit formula for the covariance function of the log-volatility in the RFSV model \eqref{formula:CovLog}, we can write a closed-form expression for a theoretical $m(q, \Delta)$:
    \begin{equation}
        m(q, \Delta) = 2\left(\var \log\sigma_{t} - \cov\left[\log\sigma_{t}, \log\sigma_{t+\Delta}\right]\right)\text{, }\footnote{\ensuremath{m(q, \Delta) = \mathbb{E}\left[(\log\sigma_{t+\Delta} - \log\sigma_{t})^2\right]}}
    \end{equation}






\section{Normality Statistical Tests}\label{sec:statisticaltest}
    In the following, $x_i$ denotes a sample of $n$ observations, $g_1$ and $g_2$ are the sample 
    skewness and kurtosis, $\mu_j$'s are the $j$-th sample central moments, and $\overline{x}$ is the 
    sample mean. 
    \subsection{D'Agostino's K-squared test}
        The sample skewness and kurtosis are defined as
        \begin{align}
            & g_1 = \frac{ m_3 }{ m_2^{3/2} } = \frac{\frac{1}{n} \sum_{i=1}^n \left( x_i - \overline{x} \right)^3}{\left( \frac{1}{n} \sum_{i=1}^n \left( x_i - \overline{x} \right)^2 \right)^{3/2}}\ , \\
            & g_2 = \frac{ m_4 }{ m_2^{2} }-3 = \frac{\frac{1}{n} \sum_{i=1}^n \left( x_i - \overline{x} \right)^4}{\left( \frac{1}{n} \sum_{i=1}^n \left( x_i - \overline{x} \right)^2 \right)^2} - 3\ .
        \end{align}
        Let
        \begin{equation}
            Z_1(g_1) = \delta \operatorname{asinh}\left( \frac{g_1}{\alpha\sqrt{\mu_2}} \right),
        \end{equation}
        where constants $\alpha$ and $\delta$ are computed as
        \begin{align}
            & W^2 = \sqrt{2\gamma_2 + 4} - 1, \\
            & \delta = 1 / \sqrt{\ln W}, \\
            & \alpha^2 = 2 / (W^2-1),
        \end{align}
        and
        \begin{equation}
            Z_2(g_2) = \sqrt{\frac{9A}{2}} \left\{1 - \frac{2}{9A} - \left(\frac{ 1-2/A }{ 1+\frac{g_2-\mu_1}{\sqrt{\mu_2}}\sqrt{2/(A-4)} }\right)^{\!1/3}\right\},  
        \end{equation}
        where
        \begin{align}
            & A = 6 + \frac{8}{\gamma_1} \left( \frac{2}{\gamma_1} + \sqrt{1+4/\gamma_1^2}\right), \\
            & \mu_1(g_2) = - \frac{6}{n+1}, \\
            & \mu_2(g_2) = \frac{ 24n(n-2)(n-3) }{ (n+1)^2(n+3)(n+5) }, \\
            & \gamma_1(g_2) \equiv \frac{\mu_3(g_2)}{\mu_2(g_2)^{3/2}} = \frac{6(n^2-5n+2)}{(n+7)(n+9)} \sqrt{\frac{6(n+3)(n+5)}{n(n-2)(n-3)}},  \label{eq:gamma1}\\
            & \gamma_2(g_2) \equiv \frac{\mu_4(g_2)}{\mu_2(g_2)^{2}}-3 = \frac{ 36(15n^6-36n^5-628n^4+982n^3+5777n^2-6402n+900) }{ n(n-3)(n-2)(n+7)(n+9)(n+11)(n+13) }\label{eq:gamma2}.
        \end{align}
        The analytical expressions for skewness and kurtosis \eqref{eq:gamma1} - \eqref{eq:gamma2} were derived by E. Pearson in \cite{Pearson1931}.
        \begin{definition}
            The \emph{D'Agostino-Pearson} statistic is defined as 
            \begin{equation}
                K^2 = Z_1(g_1)^2 + Z_2(g_2)^2
            \end{equation}
            Null hypothesis: the sample is normally distributed.
        \end{definition}

        \begin{nb}
            The $K^2$ statistic is able to detect deviations from both skewness and kurtosis. 
            If the null hypothesis is true, then the test statistic has the $\chi^2$ 
            distribution with $2$ degrees of freedom. 
        \end{nb}

    \subsection{Shapiro-Wilk test}
        \begin{definition}
            The Shapiro–Wilk test statistic is defined as
            \begin{equation}
                W = \frac{\left(\sum_{i=1}^n a_i x_{(i)}\right)^2}{\sum_{i=1}^n (x_i-\overline{x})^2},
            \end{equation}
            where
            \begin{equation*}
                (a_1, \dots, a_n) = \frac{m^{T} V^{-1}}{C}, \quad C = \| V^{-1} m \| = (m^{T} V^{-1}V^{-1}m)^{1/2},
            \end{equation*}
            and $m = (m_1, \dots, m_n)^{T}$ is a mean of order statistic from a normally distributed sample, $V$ is the covariance matrix of those normal order statistics. 
            Null hypothesis: the sample is normally distributed.
        \end{definition}

        \begin{nb}
            The $W$ statistic has no distinguishable name, and the cutoff values are calculated numerically by Monte-Carlo simulation.
        \end{nb}